Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 paper1.tex
chapter 5 parameters

The generated phase-space points are fed to the {\NJet} package \cite{Badger:2012pg} to calculate colour and helicity summed tree-level matrix elements. 
All external legs have been considered to be massless. 
The strong coupling constant has been set to $\alpha_{s} = 0.118$\footnote{This choice of
the coupling is only valid for $\mu_{R}^{2} = m_{Z}^{2}$ and ideally,
$\alpha_{s}$ should have been evaluated at the scale $\mu_{R} = 1000$ GeV. This change would result
in slightly different plots, but does not affect the validity of the key findings
of this chapter.}, and the electromagnetic coupling constant has been set to $\alpha_{e} = 1.0 / 132.5070$.
The mass of the $Z$-boson is taken to be $m_{Z} = 91.188$ GeV.
These parameters and those not listed, are consistent with those in the Standard Model mode of \aNLO \cite{Alwall:2014hca}.

>>>>

The generated phase-space points are fed to the {\NJet} package \cite{Badger:2012pg} to calculate colour and helicity summed tree-level matrix elements. 
All external legs have been considered to be massless. 
The strong coupling constant has been set to $\alpha_{s} = 0.118$\footnote{This choice of
the coupling is only valid for $\mu_{R}^{2} = m_{Z}^{2}$ and ideally,
$\alpha_{s}$ should have been evaluated at the scale $\mu_{R} = 1000$ GeV. This change would result
in slightly different plots, but does not affect the validity of the key findings
of this chapter.}, and the electromagnetic coupling constant has been set to $\alpha_{e} = 1.0 / 132.5070$.
The mass of the $Z$-boson is taken to be $m_{Z} = 91.188$ GeV.
Below we quote the full set of parameters entering the computer code
used to evaluate matrix elements. We do not quote the renormalisation
scale as it does not affect the value of tree-level matrix elements.
\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
        \toprule
        Parameters & \\
        \midrule
        Masses & \makecell[l]{$m_{b} = 4.7$ GeV \\ $m_{t} = 173$ GeV \\ $m_{\tau} = 1.777$ GeV \\ $m_{Z} = 91.188$ GeV \\ $m_{W} = 80.419$ GeV \\ $m_{H} = 125$ GeV} \\
        \midrule
        Couplings & \makecell[l]{$\alpha_{s} = 0.118$ \\ $\alpha_{e} = 1/132.507$ \\ $G_{F} = 1.166390 \times 10 ^{-5}$ GeV$^{-2}$} \\
        \midrule
        Decay widths & \makecell[l]{$\Gamma_{t} = 1.4915$ GeV \\ $\Gamma_{Z} = 2.441404$ GeV \\ $\Gamma_{W} = 2.0467$ GeV \\ $\Gamma_{H} = 6.382339 \times 10^{-3}$ GeV} \\
        \bottomrule
        \end{tabular}
    \caption{List of parameters for the matrix element generation. Masses and decay widths not listed explicitly have been set to zero.}
    \label{table:fame1_params}
\end{table}
